\documentclass{article}
\usepackage{standalone}
\usepackage{import}
\import{./}{preamble}

\begin{document}

\section{Discussion Questions}
Before each class meeting you will complete the assigned reading (see the course calendar). Based on the readings for the week you will prepare a statement of approximately two paragraphs (300 words, more is welcome) that connect two different resources together: two readings, one of the readings and your personal experience, one of the readings and another resource that was not assigned. I may post specific discussion questions that you may address as well. You will post this to the class Blackboard discussion forum under the appropriate week at the latest 2 hours before class. After class (during which we may discuss some of these posts) you will read through the paragraphs that others have submitted, and respond to at least one of them.

\section{Final Grades}
The grades will be based for 40\% on your participation in the discussions in class, for 20\% on your participation in the discussions on Blackboard, and 40\% on your final project/paper.

\section{Accommodations}
It is the policy of The College of William \& Mary to accommodate students with disabilities and qualifying diagnosed conditions in accordance with federal and state laws. Any student who feels he or she may need an accommodation based on the impact of a learning, psychiatric, physical or chronic health diagnosis should contact the Student Accessibility Services staff at 757-221-2509 or at \href{mailto:sas@wm.edu}{sas@wm.edu}. SAS staff will work with you to determine if accommodations are warranted, and if so, to help you obtain an official letter of accommodation. For more information please see \href{http://www.wm.edu/sas}{Student Accessibility Services}.

If you feel that there is anything that I can do to ensure a better learning environment for you, please do not hesitate to contact me. As long as these ad-hoc accommodations do not unfairly disadvantage other students, I am more than willing to help out.

\end{document}
